\pagenumbering{Roman}



\begin{thebibliography}{99}


\bibitem{DiffaxPaper} Treacy M.M.J., Newsam J.M. and Deem M.W. A general recursion method for calculating diffracted intensities from crystals containing planar faults. \textit{Proc. R. Soc. Lond. A}, 433:499-520, 1991. 

\bibitem{DiffaxDownload} Treacy M.M.J., Newsam J.M. and Deem M.W. DIFFaX. Available at: \url{http://www.public.asu.edu/~mtreacy/DIFFaX.html}. 

\bibitem{CrysFMLPaper} Rodr$\acute{\i}$guez-Carvajal J. and Gonzalez-Platas J., Crystallographic Fortran 90 modules library (CrysFML): a simple toolbox for crystallographic computing programs. \textit{IUCr CompComm. Newsletter}, 1:50-58, 2003. Available at: \url{http://www.iucr.org/iucr-top/comm/ccom/newsletters/}. 

\bibitem{CrysFMLDownload} Rodr$\acute{\i}$guez-Carvajal J. and Gonzalez-Platas J., CrysFML repository. Available at: \url{http://forge.epn-campus.eu/projects/crysfml/repository/}.

\bibitem{DiffaxMaths} Treacy M.M.J., Deem M.W., and Newsam J.M. DIFFaX Manual, 2005, Chap 8: How DIFFaX works (p48). Available at: \url{http://www.public.asu.edu/~mtreacy/DIFFaX$\_$manual.pdf}. 

\bibitem{Hend1942} Hendricks S. and Teller E. X-ray interference in partially ordered layer lattices. \textit{J. Chem. Phys.}, 10:147-167, 1942.

\bibitem{FAULTSPaper1} Casas-Cabanas M., Rodr$\acute{\i}$guez-Carvajal J., Palac$\acute{\i}$n M.R., \textit{Z. Kristallogr. Suppl.}, 23:243-248, 2006. 

\bibitem{FAULTSPaper2} Casas-Cabanas M., Rikarte Ormazabal J., Reynaud M., Rodr$\acute{\i}$guez-Carvajal J., \textit{in preparation}.

\bibitem{FPDownload} Rodr$\acute{\i}$guez Carvajal J., FullProf Suite. Available at: \url{http://www.ill.eu/sites/fullprof}.

\bibitem{FPPaper} Rodr$\acute{\i}$guez Carvajal J., Physica B.(1993), 192, Recent advances in magnetic structure determination by neutron powder 
diffraction. \textit{Physica B.}, 192:55-69, 1993.

\bibitem{FPManual} Rodr$\acute{\i}$guez Carvajal J., FullProf Manual. Available at \url{http://www.ill.eu/sites/fullprof/php/tutorials.html}.

\bibitem{DiffaxManual} Treacy M.M.J., Deem M.W., and Newsam J.M. DIFFaX Manual, 2005. Available at: \url{http://www.public.asu.edu/~mtreacy/DIFFaX$\_$manual.pdf}. 

\bibitem{FPSDownload} Rodr$\acute{\i}$guez Carvajal J. and Chapon L., FullProf Studio. Available at \url{http://www.ill.eu/sites/fullprof/index.html}.

\bibitem{FPSManual} Rodr$\acute{\i}$guez Carvajal J. and Chapon L., FullProf Studio Manual. Available at \url{http://www.ill.eu/sites/fullprof/index.html}.

\bibitem{VESTApaper} Momma K. and Izumi F. VESTA3 for three-dimensional vizualization of crystal, volumetric and morphology data. \textit{Journal of Applied Crystallography}, 44:1272-1276, 2011.

\bibitem{VESTAwebsite} Momma K. and Izumi F., VESTA (Visualization for Electronic and STrcutural Analysis). Available at \url{http://jp-minerals.org/vesta/en/}.

\bibitem{imageJ} \url{http://imagej.nih.gov/ij/index.html}

\bibitem{WinplotrPaper} Roisnel T. and Rodr$\acute{\i}$guez Carvajal J., WinPLOTR: A windows tool for powder diffraction pattern analysis. \textit{Mater Sci Forum}, 378(3):128-123, 2000.

\bibitem{Whit2004} Whittingham M. S., Lithium Batteries and Cathode Materials. \textit{Chemical Reviews}, 104:4271-4301, 2004. 

\bibitem{Crog2000} Croguennec L., Pouillerie C., Mansour A. N. and Delmas C., Structural characterisation of the highly deintercalated Li$_{x}$Ni$_{1.02}$O$_{2}$ phases (with x$\leq$0.30). \textit{Journal of Materials Chemistry}, 11:131-141, 2000.



\end{thebibliography}
